Evaluating infectious disease forecasts with allocation scoring rules

### 2023-03-31 alloscore_manuscript/allocation.rmd
some reorg...

>>>>

\textbf{1st attempt by APG to rephrase last paragraph}

A key observation here is that the Bayes act results from using a \textbf{shared} probability level, $1 - \lambda^{\star}/L$, to determine allocations as the corresponding quantiles of the location-specific forecast distributions $F_i$ which sum to the constraint $K$.
